FictionEro2 - Affective Impact of Fiction

### 2025-06-30 study2/analysis/2_emotion.qmd
minor

stars1b <- data.frame(label=c("*"),
                    Gender=fct_relevel(c("Male"), "Male"),
                    Outcome=c("Arousal"),
                    x=1,
                    y=0.60)

@@

>>>>

@@

pred1 <- modelbased::estimate_means(m_arousal, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
  as.data.frame() |> 
  mutate(Outcome="Arousal")

stars1b <- data.frame(label=c("*"),
                    Gender=fct_relevel(c("Male")),
                    Outcome=c("Arousal"),
                    x=1,
                    y=0.60)

pred1 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
  ggplot(aes(x=StimuliType, y=Proportion)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.3), alpha=0.8, linewidth=1, key_glyph = "path") +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.3), size=0.6) +
  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=6) +
  # geom_rect(data=data.frame(StimuliType = "Individual", Proportion=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.7), color="#8BC34A", alpha=0, linewidth = 1) +
  # geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0, linewidth = 1) +
  facet_grid(Outcome~Gender, switch="y", scales ="free") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent, expand = c(0,0)) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("#1C2133"), color=NA),
        strip.text.x = element_text(size = 12, color = "White", face = "bold"),
        strip.text.y = element_blank(),
        axis.text.x = element_text(size=12, color="black", face = "bold"),
        legend.text = element_text(size = 12),
        legend.position = "bottom") +
  labs(color="Images presented as:")
